\documentclass[8pt]{beamer}
\setbeamertemplate{navigation symbols}{}

\usepackage{multicol}
\usepackage{graphicx}
\usepackage{soul}
\graphicspath{ {images/} }


\begin{document}

%Title pages
\title{Ex vs. Teco}
\author{Brandon Moore and John Markiewicz}
\date{}

\begin{frame}
	\titlepage
\end{frame}

\title{Neo-Vim vs Spacemacs}
\author{Brandon Moore and John Markiewicz}
\date{}

\begin{frame}
	\titlepage
\end{frame}
%End title pages

\title{Vim vs. Emacs}
\author{Brandon Moore and John Markiewicz}
\date{}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}
	\frametitle{C-x M-c M-butterfly}
  \begin{quote}
    Emacs is a great operating system, lacking only a decent editor
  \end{quote}
	\begin{flushright}
		--Anonymous
	\end{flushright}
\end{frame}
\note{A vim-user's view of Emacs is that the editor has a heavy amount of features, but lacks a focus on actually editing and tries to do everything under the sun.}

\begin{frame}
	\frametitle{vi vi vi}
  \begin{quote}
    Using a free version of vi is not a sin but a penance.
  \end{quote}
  \begin{flushright}
	\only<1>{--Richard Stallman, head of the Church of Emacs\\}
	\only<2>{--\st{Richard Stallman, head of the Church of Emacs}\\}
	\only<2>{--Saint IGNUcious, head of the Church of Emacs}
  \end{flushright}
\end{frame}
\note{Emacs view on Vim: it's fine to use, but why limit yourself like that?}

\begin{frame}
				\frametitle{A historic holy war\\Emacs vs. Vi(m)}
  \begin{itemize}
  \item TECO(1962) $\rightarrow$ Emacs(1976) $\rightarrow$ GNU Emacs(1985) $\rightarrow$ Spacemacs
	\item Ex(1976) $\rightarrow$ Vi(1976) $\rightarrow$ Vim(1991) $\rightarrow$ NeoVim
  \end{itemize}
\end{frame}
\note{History of the editors}

\begin{frame}
  \frametitle{Let's look at Vim}
\end{frame}
\note{Demonstrate Vim}

\begin{frame}
  \frametitle{Let's look at Emacs}
\end{frame}
\note{Demonstrate Emacs}

\begin{frame}
  \frametitle{Why use Vim?}
  \begin{multicols}{2}
    \textbf{Pros of Vim}
    \begin{itemize}
    \item Customizable
		\item Rich library of extensions
		\item Constantly improving
		\item Portable
		\item ...in multiple ways
    \end{itemize}
    \columnbreak
    \textbf{Cons of Emacs}
    \begin{itemize}
    \item Reliant on customization
		\item Comes with bloat
		\item Hello Carpal Tunnel
		\item Tries to do too much
    \end{itemize}
  \end{multicols}
\end{frame}
\note{Malide's pro con slide}

\begin{frame}
  \frametitle{Why use Emacs?}
  \begin{multicols}{2}
    \textbf{Pros of Emacs}
    \begin{itemize}
    \item Flexible, powerful, pleasant to use language for adding
      features (elisp).
    \item Features.
    \item Compatibility with the past few decades' worth of software
    \item Org-mode
    \item Evil-mode for those used to vim keybindings
    \end{itemize}
    \columnbreak
    \textbf{Cons of Vim}
    \begin{itemize}
    \item Community fragmentation (Neovim vs Vim 8.0) and
      incompatibility between versions.
    \item Fewer features.
    \item Vimscript.
    \item Inconsistent async methods between Vim 8 and Neovim.
    \item Performance issues with syntax highlighting/line
      numbers/large files.
    \end{itemize}
  \end{multicols}
\end{frame}
\note{EDT's pro con slide}

\begin{frame}
	\frametitle{stdlinux (and problems with old systems)}
	\begin{itemize}
		\item stdlinux is old and out of date. vim and emacs don't work well
		\item a basic .vimrc is needed to use vim on stdlinux
		\item It should be updated soon!
	\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{How to learn}
  \textbf{Vim}
  \begin{itemize}
	\item vim help pages (via :help <topic>)
  \item \$vimtutor
  \item http://www.openvim.com/
  \end{itemize}
  \textbf{Emacs}
  \begin{itemize}
  \item Emacs help features (internal documentation accessible via C-h C-a)
  \item Emacs wiki
  \item Worg (for org-mode)
  \end{itemize}
\end{frame}
\note{List of resources}

\end{document}
